### 2015-03-07 Gozde-Liora-Replication-Code.Rmd
Preliminary output for Model and Table1

---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---

# Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)

# Run necessary packages and load data (Source: Arzheimer dataverse)

```{r}
library(Zelig)
library(lme4)
library(MASS)
library(nlme)
library(plm)
library(xtable)
library(foreign)
library(dplyr)
library(broom)
library(ggplot2)

data <- read.dta("nonimp.dta")
```

# Clean data and rename variables ???????

```{r}

```

# Plot Data

```{r}
ggplot(data, aes(x=zsur, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) # Relationship with standardized unemployment rate

ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w immigration

ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w welfare (=unemp benefit)
```

# Create centered variables for Saliance and Variance based on grand mean centering according to author

```{r}
data <- data  %>% 
  mutate(salienzmean.c = (salienzmean - 3.84568))%>% 
  mutate(rvar.c = rvar - 21.75423)
```

# Make male variable numeric

```{r}
data <- data %>%
  mutate(male = as.numeric(male))
```

# Create a dummy variable for country (transform from character to factor variable)

```{r}
data <- data %>%
  mutate(country = factor(sortcountry, labels=c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
```

# Run the regression (multilevel logictic regresstion based on Quasi-penalized likelihood): All contextual variables are mean-centered (as z- connotes)

```{r}
model1 <- glmmPQL(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, random=~1|kontext, family=binomial(link="logit"), data=data, verbose=TRUE)
summary(model1)

```

# Visualize regression outputs???????

```{r}
library(car)
# Diagnostic 1: Residual Plots
# residualPlots(out.pql)

```

#Table 1

```{r}
# Create vectors of coefficients, standard deviations, and variable names
coef_vec <- as.vector(model1$coef$fixed) 
N <- c(174452, 267)

sd_vec <- as.vector(sqrt(diag(model1$varFix))) #Vector of sds
var_names <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

# Create matrix of coefficients and standard deviations.

table_matrix <- cbind(coef_vec, sd_vec)

##Label matrix.

rownames(table_matrix) <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

x <- xtable(table_matrix, digits = 3)
print.xtable(x, type = "html", file="tablepractice.html")

### 2015-03-09 Gozde-Liora-Replication-Code.Rmd

@@
 library(ggplot2)
-
+library(xtable)
+library(stargazer)
 data <- read.dta("nonimp.dta")
-```
-
-# Clean data and rename variables ???????
-
-```{r}
-
-```
-
-# Plot Data
-
-```{r}
-ggplot(data, aes(x=zsur, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) # Relationship with standardized unemployment rate
-
-ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w immigration
-
-ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w welfare (=unemp benefit)
 ```
@@
 
-# Run the regression (multilevel logictic regresstion based on Quasi-penalized likelihood): All contextual variables are mean-centered (as z- connotes)
+# Plot Data
+
+```{r}
+ggplot(data, aes(x=zsur, y=rexvote)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se=FALSE) # Relationship w/ standardized unemployment rate
+
+ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method= "glm", family = "binomial", se=FALSE) # Relationship w/ immigration
+
+ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w/ welfare (=unemp benefit)
+```
+
+# Run the regression (multilevel logictic regression based on Quasi-penalized likelihood): All contextual variables are mean-centered (as connoted by "z-")
 
@@
 # Create vectors of coefficients, standard deviations, and variable names
-coef_vec <- as.vector(model1$coef$fixed) 
-N <- c(174452, 267)
 
-sd_vec <- as.vector(sqrt(diag(model1$varFix))) #Vector of sds
+Coefficient <- as.vector(model1$coef$fixed) 
+n <- c(174452, 267)
+
+Standard_Deviation <- as.vector(sqrt(diag(model1$varFix)))
+
 var_names <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")
@@
 
-table_matrix <- cbind(coef_vec, sd_vec)
+table_matrix <- cbind(Coefficient, Standard_Deviation)
 
@@
 
-rownames(table_matrix) <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")
+rownames(table_matrix) <- c("Male","18_29 years","30_45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers x Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")
 
-x <- xtable(table_matrix, digits = 3)
+# Create table using xtable
+
+x <- xtable(table_matrix, digits = 3, caption = "Logistic multilevel model. PQL2 estimates, model-based standard errors in parentheses. MI results based on 11 separate imputations.")
 print.xtable(x, type = "html", file="tablepractice.html")
+
+# Create Table 1 using stargaze
+
+stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model.
+PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)

### 2015-03-09 Replication Code.R
Rename Replication Code.R to Harvard students replication.R

@@ -1,349 +1,0 @@
-##Replication Code for "The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002"
-##Jeffrey Javed and Noam Gidron
-##May 8, 2011
-
-##Load libraries.
-
-library(Zelig)
-library(lme4)
-library(MASS)
-library(nlme)
-library(plm)
-library(xtable)
-
-##Load Arzheimer (2009) data.
-
-data <- as.data.frame(read.delim("nonimp.tab.tsv"))
-
-##Center variables (done as according to the author).
-
-salienzmean.c <- data$salienzmean - 3.84568
-rvar.c <- data$rvar - 21.75423
-
-##Create country dummies.
-
-country <- factor(data$sortcountry, labels=c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE"))
-
-##Run with PQL.
- 
-out.pql <- glmmPQL(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zsur:zreplacementrate + zasylumseekers:zreplacementrate + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, random=~1|kontext, family=binomial(link="logit"), data=data, verbose=TRUE)
-
-summary(out.pql)
-
-####Simulations for the Original Model with Centered Variables##
-
-##Simulate betas for centered data set.
-
-set.seed(02138)
-simbetas <- mvrnorm(n=10000, mu=out.pql$coef$fixed, Sigma=out.pql$var)
-
-##Create matrix for all variables.
-
-mat1 <- cbind(data$rexvote, data$male, data$age1, data$age2, data$age4, data$mye1, data$mye2, data$farmerown, 
-data$worker, data$retired, data$unemployed, data$zlrs, data$euschlecht, data$zsatisdmo, data$disp, data$lfed1, 
-data$zasylumseekers, data$zsur, data$zreplacementrate, data$rmax, salienzmean.c, rvar.c, data$at, data$be, data$deo, 
[…]

### 2015-03-11 Gozde-Liora-Replication-Code.Rmd
figure 1 first part

@@
 
+# Model 2 based on glm logit
+
+```{r}
+model2 <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, family=binomial(link="logit"), data=data, verbose=TRUE)
+summary(model2)
+
 # Visualize regression outputs???????
@@
 PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
+
+```
+
+# Figure 1 (Conditonal Effects of Unemployment and Immigration)
+
+```{r}
+library(msm)
+asy <- seq(from = -.98, to=4.46, by=.01) # vector with possible values for asylumseekers
+slopes <- model1$coef$fixed[17] + model1$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
+estmean <- model1$coef$fixed # Estimated means for each variable 
+var <- vcov(model1)
+se <- rep(NA, length(asy))
+
+for (i in 1:length(asy)) {
+  j <- asy[i]
+  se[i] <- deltamethod (~ (x17) + (x36)*j, estmean, var)
+}
+
+upper <- slopes + 1.96*se
+lower <- slopes - 1.96*se
+asy.data <- cbind(asy, slopes, upper, lower)
+plot(asy, slopes, type = "l", lty = 1, ylim=c(-.2, .2), xlim=c(-2, 4), ylab= "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
+points(asy, upper, type = "l", lty = 2)
+points(asy, lower, type = "l", lty = 2)
+points(asy, rep(0, length(asy)), type = "l", col = "black")
+```

### 2015-03-12 Gozde-Liora-Replication-Code.Rmd
ggplot figure added

@@
 }
-
+# Create confidence intervals and combine all values in matrix.
 upper <- slopes + 1.96*se
@@
 asy.data <- cbind(asy, slopes, upper, lower)
+
+# Creating the first graph in base R
+
 plot(asy, slopes, type = "l", lty = 1, ylim=c(-.2, .2), xlim=c(-2, 4), ylab= "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
@@
 points(asy, rep(0, length(asy)), type = "l", col = "black")
+
+# Creating the same graph with ggplot - much better looking.
+
+asy.data <- data.frame(asy.data) # Turn matrix into data frame so that ggplot can read it.
+xtitle <- "Asylumseekers"
+ytitle <- "Effect: Unemployment"
+main <- "The Conditional Effects of Unemployment and Immigration"
+ggplot(asy.data, aes(x=asy, y=slopes)) + 
+  geom_line(aes(y=slopes), color="blue") + 
+  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.2) + 
+  geom_hline(yintercept=0, size=0.4, color="black") +
+  labs(x=xtitle, y=ytitle, title=main)
+
 ```

### 2015-03-13 Gozde-Liora-Replication-Code.Rmd
updated with clean data/code and added Figure 1

--- 2015-03-09 Gozde-Liora-Replication-Code.Rmd
@@
 library(stargazer)
+
 data <- read.dta("nonimp.dta")
+
+# Cleaning up data
+data <- rename(data, ext_vote = rexvote)
+data <- rename(data, age_1 = age1) # Age (16-25)
+data <- rename(data, age_2 = age2) # Age 
+data <- rename(data, age_4 = age4) # Age (65- )
+data <- rename(data, edu_1 = mye1) 
+data <- rename(data, edu_2 = mye2)
+data <- rename(data, age_2 = age2)
+data <- rename(data, farmer_own = farmerown)
+data <- rename(data, left_right_scale = zlrs)
+data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
+data <- rename(data, z_dem_satis = zsatisdmo) 
+data <- rename(data, dispro_elect = disp) 
+data <- rename(data, federalism = lfed1)
+data <- rename(data, z_asylumseeker = zasylumseekers)
+data <- rename(data, z_unemp = zsur) 
+data <- rename(data, z_replacement = zreplacementrate) 
+data <- rename(data, max_er = rmax)
+
 ```
@@
 data <- data  %>% 
-  mutate(salienzmean.c = (salienzmean - 3.84568))%>% 
-  mutate(rvar.c = rvar - 21.75423)
+  mutate(salience_mean_c = (salienzmean - 3.84568)) %>% 
+  mutate(var_c = rvar - 21.75423)
 ```
@@
 data <- data %>%
-  mutate(country = factor(sortcountry, labels=c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
+  mutate(country = factor(sortcountry, labels = c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
 ```
 
-# Plot Data
+# Plot Data for exploration
 
 ```{r}
-ggplot(data, aes(x=zsur, y=rexvote)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se=FALSE) # Relationship w/ standardized unemployment rate
+ggplot(data, aes(x = z_unemp, y = ext_vote)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se = FALSE) # Relationship w/ standardized unemployment rate
 
-ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method= "glm", family = "binomial", se=FALSE) # Relationship w/ immigration
+ggplot(data, aes(x = z_asylumseeker, y = ext_vote, color = country)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se = FALSE) # Relationship w/ immigration
 
-ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w/ welfare (=unemp benefit)
+ggplot(data, aes(x = z_replacement, y = ext_vote, color = country)) + geom_point() + geom_smooth(method = lm, se = FALSE) #Relationship w/ welfare (=unemp benefit)
 ```
 
-# Run the regression (multilevel logictic regression based on Quasi-penalized likelihood): All contextual variables are mean-centered (as connoted by "z-")
+# Run the regression (multilevel logictic regression based on Quasi-penalized likelihood): All contextual variables are standardized mean-centered (as connoted by "z-")
 
 ```{r}
+model <- glmmPQL(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + left_right_scale + eu_neg + z_dem_satis + dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1, random = ~1|kontext, family = binomial(link = "logit"), data = data, verbose = TRUE)
+summary(model)
+
 model1 <- glmmPQL(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, random=~1|kontext, family=binomial(link="logit"), data=data, verbose=TRUE)
@@
 
-# Visualize regression outputs???????
+# Model 2 based on glm logit - comparison
 
 ```{r}
-library(car)
-# Diagnostic 1: Residual Plots
-# residualPlots(out.pql)
+model2 <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, family=binomial(link="logit"), data=data, verbose=TRUE)
+summary(model2)
 
@@
 
-Coefficient <- as.vector(model1$coef$fixed) 
+coefficient <- as.vector(model$coef$fixed) 
 n <- c(174452, 267)
 
-Standard_Deviation <- as.vector(sqrt(diag(model1$varFix)))
+stand_dev <- as.vector(sqrt(diag(model$varFix)))
 
@@
 
-table_matrix <- cbind(Coefficient, Standard_Deviation)
+table_matrix <- cbind(coefficient, stand_dev)
 
@@
 PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
+
+```
+
+# Figure 1 (Conditonal Effects of Unemployment and Immigration)
+
+```{r}
+library(msm)
+asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
+variable <- asy
+slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
+estmean <- model$coef$fixed # Estimated means for each variable 
+var <- vcov(model)
+se <- rep(NA, length(asy))
+
+for (i in 1:length(variable)) {
+  j <- variable[i]
+  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, var)
+}
+# Create confidence intervals and combine all values in matrix.
+upper <- slopes + 1.96 * se
+lower <- slopes - 1.96 * se
+variable.data <- cbind(variable, slopes, upper, lower)
+
+# Creating the first graph in base R 
+par(mfrow = c(2, 1))
+plot(variable, slopes, type = "l", lty = 1, ylim = c(-.2, .2), xlim = c(-2, 4), ylab = "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
+points(variable, upper, type = "l", lty = 2)
+points(variable, lower, type = "l", lty = 2)
+points(variable, rep(0, length(variable)), type = "l", col = "black")
+
+# Creating the same graph with ggplot - much better looking.
+
+variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
+xtitle <- "Asylumseekers"
+ytitle <- "Effect: Unemployment"
+main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
+graph1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") +
+  labs(x = xtitle, y = ytitle, title = main)
+
+#Figure 1, graph 2
+
+unemployment <- seq(from = -5.908098, to = 12.291902, by = .01) # vector with possible values for unemployment
+variable <- unemployment
+slopes <- model$coef$fixed[16] + model$coef$fixed[36] * variable # Estimated slopes based on estimated coefficients of unemployment (16) and unemployment x immigration (36)
+estmean <- model$coef$fixed # Estimated means for each variable 
+var <- vcov(model)
+se <- rep(NA, length(variable))
+
+for (i in 1:length(variable)) {
+  j <- variable[i]
+  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, var)
+}
+# Create confidence intervals and combine all values in matrix.
+upper <- slopes + 1.96 * se
+lower <- slopes - 1.96 * se
+variable.data <- cbind(variable, slopes, upper, lower)
+
+# Creating the first graph in base R
+
+plot(variable, slopes, type = "l", lty = 1, ylim=c(-.4, .6), xlim=c(-5, 15), ylab= "Effect: Asylum seekers", xlab = "Unemployment", main = "The Conditional Effects of Unemployment and Immigration")
+points(variable, upper, type = "l", lty = 2)
+points(variable, lower, type = "l", lty = 2)
+points(variable, rep(0, length(variable)), type = "l", col = "black")
+
+# Creating the same graph with ggplot:
+
+variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
+xtitle <- "Unemployment"
+ytitle <- "Effect: Asylum seekers"
+main <- "The Conditional Effects of Unemployment and Immigration"
+graph2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") +
+  labs(x = xtitle, y = ytitle)
+
+# Figure 1 with ggplot
+library(grid)
+library(gridExtra)
+grid.arrange(graph1, graph2, ncol = 1)
+
+```
+
+```{r}
+
+# Figure 2, graph 1 (Conditonal Effects of Salience and Variance)
+
+salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
+variable <- salience
+slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
+estmean <- model$coef$fixed # Estimated means for each variable 
+var <- vcov(model)
+se <- rep(NA, length(variable))
+
+for (i in 1:length(variable)) {
+  j <- variable[i]
+  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, var)
+}
+# Create confidence intervals and combine all values in matrix.
+upper <- slopes + 1.96*se
+lower <- slopes - 1.96*se
+variable.data <- cbind(variable, slopes, upper, lower)
+
+# Creating the first graph in base R
+
+plot(variable, slopes, type = "l", lty = 1, ylim=c(-.02, .03), xlim=c(-5, 20), ylab= "Effect: Variance", xlab = "Salience", main = "The Conditional Effects of Salience and Variance")
+points(variable, upper, type = "l", lty = 2)
+points(variable, lower, type = "l", lty = 2)
+points(variable, rep(0, length(variable)), type = "l", col = "black")
+
+# Creating the same graph with ggplot - much better looking.
+library(ggplot2)
+variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
+xtitle <- "Salience"
+ytitle <- "Effect: Variance"
+main <- "The Conditional Effects of Salience and Variance"
+graph3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") +
+  labs(x = xtitle, y = ytitle, title = main)
+```

### 2015-03-16 Gozde-Liora-Replication-Code.Rmd
replication submission

@@
 
+Note: Please refer to saved files in our repository for images from the article.
+Also please refer to the table and figures (Table 1, Figure 1, 2) in the repository.
+Image scales are rearranged in saved versions.
+Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood.
+Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
+
+#The paper
+Kai Arzheimer, "Contextual Factors and the Extreme Right Vote in Western Europe, 1980-2002"25548117.pdf
+This article attempts to answer the “twin question of why the extreme right support is so unstable within many countries over time, and why these parties are so weak in many West European countries.” Authors conduct a multi-level analysis, combining data on macro-level contextual variables (unemployment, immigration, and welfare benefits) with individual-level variables (sociodemographic factors and attitudes).
+
+#The data
+Individual-level variables come from Eurobarometer surveys (1980-2002), while contextual variables are gathered from a number of different data sets produced by the OECD, UNHCR etc.
+The merged data and the Stata code are available through the author’s dataverse at: http://hdl.handle.net/1902.1/12092.
+
+#The model 
+The article uses a logistic multi-level model via Penalized Quasi-Likelihood. The dependent variable is vote intention for an extreme right party, which is assumed to be binomially distributed.
+
 # Run necessary packages and load data (Source: Arzheimer dataverse)
@@
 ```{r}
-library(Zelig)
-library(lme4)
+
 library(MASS)
 library(nlme)
-library(plm)
 library(xtable)
@@
 library(stargazer)
+library(grid)
+library(gridExtra)
 
@@
 data <- rename(data, ext_vote = rexvote)
-data <- rename(data, age_1 = age1) # Age (16-25)
-data <- rename(data, age_2 = age2) # Age 
-data <- rename(data, age_4 = age4) # Age (65- )
-data <- rename(data, edu_1 = mye1) 
-data <- rename(data, edu_2 = mye2)
-data <- rename(data, age_2 = age2)
+data <- rename(data, age_1 = age1) # (18–29 years)
+data <- rename(data, age_2 = age2) # (30–45 years)
+data <- rename(data, age_4 = age4) # (>65 years)
+data <- rename(data, edu_1 = mye1) # Education: middle/high
+data <- rename(data, edu_2 = mye2) # Education: university
 data <- rename(data, farmer_own = farmerown) 
-data <- rename(data, left_right_scale = zlrs)
+data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
 data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
-data <- rename(data, z_dem_satis = zsatisdmo) 
-data <- rename(data, dispro_elect = disp) 
-data <- rename(data, federalism = lfed1)
+data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
+data <- rename(data, dispro_elect = disp) # Disproportionality
+data <- rename(data, federalism = lfed1) # Decentralization
 data <- rename(data, z_asylumseeker = zasylumseekers) 
-data <- rename(data, z_unemp = zsur) 
-data <- rename(data, z_replacement = zreplacementrate) 
-data <- rename(data, max_er = rmax)
+data <- rename(data, z_unemp = zsur) # Unemployment rate
+data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
+data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse
 
@@
 
+# Preparing data for analysis
+
+```{r}
 # Create centered variables for Saliance and Variance based on grand mean centering according to author
 
-```{r}
 data <- data  %>% 
@@
   mutate(var_c = rvar - 21.75423)
-```
 
 # Make male variable numeric
-
-```{r}
 data <- data %>%
   mutate(male = as.numeric(male))
-```
 
 # Create a dummy variable for country (transform from character to factor variable)
-
-```{r}
 data <- data %>%
   mutate(country = factor(sortcountry, labels = c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
-```
-
-# Plot Data for exploration
-
-```{r}
-ggplot(data, aes(x = z_unemp, y = ext_vote)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se = FALSE) # Relationship w/ standardized unemployment rate
-
-ggplot(data, aes(x = z_asylumseeker, y = ext_vote, color = country)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se = FALSE) # Relationship w/ immigration
-
-ggplot(data, aes(x = z_replacement, y = ext_vote, color = country)) + geom_point() + geom_smooth(method = lm, se = FALSE) #Relationship w/ welfare (=unemp benefit)
 ```
@@
 model <- glmmPQL(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + left_right_scale + eu_neg + z_dem_satis + dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1, random = ~1|kontext, family = binomial(link = "logit"), data = data, verbose = TRUE)
-summary(model)
-
-model1 <- glmmPQL(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, random=~1|kontext, family=binomial(link="logit"), data=data, verbose=TRUE)
-summary(model1)
-
+# summary(model) # Output too long
 ```
 
-# Model 2 based on glm logit - comparison
-
-```{r}
-model2 <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, family=binomial(link="logit"), data=data, verbose=TRUE)
-summary(model2)
-
-```
-
-#Table 1
+# Table 1
 
@@
 n <- c(174452, 267)
-
 stand_dev <- as.vector(sqrt(diag(model$varFix)))
-
-var_names <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")
 
@@
 
-##Label matrix.
+# Label matrix.
 
@@
 
-# Create table using xtable
+# Create Table 1 with stargaze
 
-x <- xtable(table_matrix, digits = 3, caption = "Logistic multilevel model. PQL2 estimates, model-based standard errors in parentheses. MI results based on 11 separate imputations.")
-print.xtable(x, type = "html", file="tablepractice.html")
-
-# Create Table 1 using stargaze
-
-stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model.
+table_1 <- stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model.
 PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
@@
 asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
-variable <- asy
+variable <- asy # to standardize the code
 slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
 estmean <- model$coef$fixed # Estimated means for each variable 
-var <- vcov(model)
+var <- vcov(model) # Estimated variances
 se <- rep(NA, length(asy))
@@
 main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
-graph1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+graph_1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
   geom_line(aes(y = slopes), color = "blue") + 
@@
   geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main)
+  labs(x = xtitle, y = ytitle, title = main) +
+  coord_fixed(ratio = 8)
 
@@
 
-# Creating the first graph in base R
+# Creating second part of the figure in base R
 
@@
 main <- "The Conditional Effects of Unemployment and Immigration"
-graph2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+graph_2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
   geom_line(aes(y = slopes), color = "blue") + 
@@
   geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle)
+  labs(x = xtitle, y = ytitle) +
+  coord_fixed(ratio = 12)
 
 # Figure 1 with ggplot
-library(grid)
-library(gridExtra)
-grid.arrange(graph1, graph2, ncol = 1)
+
+grid.arrange(graph_1, graph_2, ncol = 1)
+
+# Plot separately - better scaled
+graph_1
+graph_2
 
@@
 
+# Figure 2 (Conditonal Effects of Salience and Variance)
+
 ```{r}
-
-# Figure 2, graph 1 (Conditonal Effects of Salience and Variance)
-
+# Graph 1
 salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
 variable <- salience
-slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
+slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
 estmean <- model$coef$fixed # Estimated means for each variable 
@@
 
-# Creating the same graph with ggplot - much better looking.
-library(ggplot2)
+# Creating the same graph with ggplot:
+
 variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
@@
 main <- "The Conditional Effects of Salience and Variance"
-graph3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+graph_3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
   geom_line(aes(y = slopes), color = "blue") + 
@@
   geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main)
+  labs(x = xtitle, y = ytitle, title = main) +
+  coord_fixed(ratio = 400)
+
+# Second part of Figure 2
+
+variance <- seq(from = -21.71426, to = 174.34497, by=10) # vector with possible values for variance
+variable <- variance
+slopes <- model$coef$fixed[20] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
+se <- rep(NA, length(variable))
+for (i in 1:length(variable)) {
+  j <- variable[i]
+  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, var)
+}
+# Create confidence intervals and combine all values in matrix.
+upper <- slopes + 1.96 * se
+lower <- slopes - 1.96 * se
+variable.data <- cbind(variable, slopes, upper, lower)
+
+# Creating the second graph in base R 
+par(mfrow = c(1,1))
+plot(variable, slopes, type = "l", lty = 1, ylim = c(-.05, .2), xlim = c(-50, 150), ylab = "Effect: Saliance", xlab = "Variance")
+points(variable, upper, type = "l", lty = 2)
+points(variable, lower, type = "l", lty = 2)
+points(variable, rep(0, length(variable)), type = "l", col = "black")
+
+# Creating the same graph with ggplot:
+
+variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
+xtitle <- "Variance"
+ytitle <- "Effect: Salience"
+main <- "The Conditional Effects of Salience and Variance"
+graph_4 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") +
+  labs(x = xtitle, y = ytitle, title = main) +
+  coord_fixed(ratio = 500)
+
+grid.arrange(graph_3, graph_4, ncol = 1)
+# Better scaled versions - not combined
+graph_3
+graph_4
 ```

### 2015-04-07 Gozde-Liora-Replication-Code.Rmd
updated code
replication final commit
Test for pushing problems

@@
 ---
-
+test
 # Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)
@@
 Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood.
-Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
+Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables; we'll keep working on these.
 
@@
 
-# Second part of Figure 2
+# Second part of Figure 2:
 

### 2015-04-10 Gozde-Liora-Replication-Code.Rmd
Adding images from paper to our code

@@
 # Table 1
-
+![Table 1](figures/table1.png)
 ```{r}
@@
 # Figure 1 (Conditonal Effects of Unemployment and Immigration)
-
+![Figure 1](figures/fig1.png)
 ```{r}
@@
 # Figure 2 (Conditonal Effects of Salience and Variance)
-
+![Figure 2](figures/fig2.png)
 ```{r}

### 2015-04-10 Gozde-Liora-Replication-Code.Rmd
Fixing typo from: deleting base R graphs, adding an explanation of how we wrote code for our figures to be reuseable for different variables of interest in other figures

@@
 asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
-variable <- asy # to standardize the code
+variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
 slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
@@
 
-# Creating the first graph in base R 
-par(mfrow = c(2, 1))
-plot(variable, slopes, type = "l", lty = 1, ylim = c(-.2, .2), xlim = c(-2, 4), ylab = "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
-points(variable, upper, type = "l", lty = 2)
-points(variable, lower, type = "l", lty = 2)
-points(variable, rep(0, length(variable)), type = "l", col = "black")
-
-# Creating the same graph with ggplot - much better looking.
+# Creating the first graph with ggplot
 
@@
 
-# Creating second part of the figure in base R
-
-plot(variable, slopes, type = "l", lty = 1, ylim=c(-.4, .6), xlim=c(-5, 15), ylab= "Effect: Asylum seekers", xlab = "Unemployment", main = "The Conditional Effects of Unemployment and Immigration")
-points(variable, upper, type = "l", lty = 2)
-points(variable, lower, type = "l", lty = 2)
-points(variable, rep(0, length(variable)), type = "l", col = "black")
-
-# Creating the same graph with ggplot:
+# Creating the second graph with ggplot:
 
@@
 
-# Creating the first graph in base R
-
-plot(variable, slopes, type = "l", lty = 1, ylim=c(-.02, .03), xlim=c(-5, 20), ylab= "Effect: Variance", xlab = "Salience", main = "The Conditional Effects of Salience and Variance")
-points(variable, upper, type = "l", lty = 2)
-points(variable, lower, type = "l", lty = 2)
-points(variable, rep(0, length(variable)), type = "l", col = "black")
-
-# Creating the same graph with ggplot:
+# Creating the first graph with ggplot:
 
@@
 
-# Creating the second graph in base R 
-par(mfrow = c(1,1))
-plot(variable, slopes, type = "l", lty = 1, ylim = c(-.05, .2), xlim = c(-50, 150), ylab = "Effect: Saliance", xlab = "Variance")
-points(variable, upper, type = "l", lty = 2)
-points(variable, lower, type = "l", lty = 2)
-points(variable, rep(0, length(variable)), type = "l", col = "black")
-
-# Creating the same graph with ggplot:
+# Creating the second graph with ggplot:
 

### 2015-04-23 replication.Rmd
Latest code with Gozde's edits

--- 2015-04-10 Gozde-Liora-Replication-Code.Rmd
@@
+---
 ---
@@
 ---
-test
+
 # Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)
@@
 library(msm)
-asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
+asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01)) # vector with possible values for asylumseekers
+
 variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
-slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
+slopes <- model$coef$fixed["z_unemp"] + model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
 estmean <- model$coef$fixed # Estimated means for each variable 
-var <- vcov(model) # Estimated variances
-se <- rep(NA, length(asy))
-
+estvar <- vcov(model) # Estimated covariances
+se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
+# Creating a loop using the deltamethod function which approximates standard errors of transformation of parameters based on the given estimates of the mean and covariance (~ bootstrapping).
 for (i in 1:length(variable)) {
   j <- variable[i]
-  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, var)
+  se[i] <- deltamethod (~ (x17) + (x36) * j, estmean, estvar)
 }
+
 # Create confidence intervals and combine all values in matrix.
@@
 
-unemployment <- seq(from = -5.908098, to = 12.291902, by = .01) # vector with possible values for unemployment
-variable <- unemployment
-slopes <- model$coef$fixed[16] + model$coef$fixed[36] * variable # Estimated slopes based on estimated coefficients of unemployment (16) and unemployment x immigration (36)
-estmean <- model$coef$fixed # Estimated means for each variable 
-var <- vcov(model)
-se <- rep(NA, length(variable))
-
+unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
+variable <- unemployment # standardized label
+slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
+estmean <- model$coef$fixed # Estimated means for variables 
+estvar <- vcov(model) # Estimated covariances
+se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
+# Creating a loop with deltamethod to calculate estimated standard errors
 for (i in 1:length(variable)) {
   j <- variable[i]
-  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, var)
+  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
 }
@@
 # Graph 1
-salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
+salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
 variable <- salience
-slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
-estmean <- model$coef$fixed # Estimated means for each variable 
-var <- vcov(model)
-se <- rep(NA, length(variable))
-
+slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
+estmean <- model$coef$fixed # Estimated means for variables 
+estvar <- vcov(model) # Estimated covariances
+se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
+# Creating a loop with deltamethod to calculate estimated standard errors
 for (i in 1:length(variable)) {
   j <- variable[i]
-  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, var)
+  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
 }
@@
 
-variance <- seq(from = -21.71426, to = 174.34497, by=10) # vector with possible values for variance
+variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
 variable <- variance
-slopes <- model$coef$fixed[20] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
-se <- rep(NA, length(variable))
+slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
+estmean <- model$coef$fixed # Estimated means for variables 
+estvar <- vcov(model) # Estimated covariances
+se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
+# Creating a loop with deltamethod to calculate estimated standard errors
+
 for (i in 1:length(variable)) {
   j <- variable[i]
-  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, var)
+  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
 }
@@
 graph_4
+`
 ```
+
+# Model 1: Adorno Thesis (Personality Traits and Value Orientations)
+
+```{r}
+model1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+
+```
+
+# Model 2: Parsons Thesis (Social Disintegration)
+```{r}
+model2 <- glm(ext_vote ~ eu_neg + z_dem_satis + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+```
+
+# Model 3: Group Conflict Model (Various theories)
+
+```{r}
+model3 <- glm(ext_vote ~ dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+
+```

### 2015-04-24 replication.Rmd
With three models for extension
Added paragraph explanations of theories behind each model in the extension

@@
 
+#Extension
+Our extension was inspired by Andreas Wimmer and Yuval Feinstein's 2010 paper "The Rise of the Nation-State Across the World, 1816-2001."  This paper seperately tests the prevailing explanatory theories of the rise of the nation-state as the dominant form of governance.
+Our extension takes a similar approach, testing the major theories of support for extreme right parties in the Western European context in individual models.
+We operationalize the variables in these theories using the available measures from the original data set, and each model retains the measures of salience (the prominence of extreme right issues on parties' agendas) and variance (degree of consensus within parties) and their interaction as independant variables.
+
 # Model 1: Adorno Thesis (Personality Traits and Value Orientations)
+The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.
+We operationalize "personality traits and value orientations" using the individual level characteristics from our data set.
 
@@
 # Model 2: Parsons Thesis (Social Disintegration)
+Parsons' 1942 theory of social disintegratoin posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.
+While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change (satisfaction with democracy, opinions about the European Union) that Parsons refers to.
+
 ```{r}
@@
 # Model 3: Group Conflict Model (Various theories)
+Group conflict theories encompass a variety of theories.
+Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits.
+Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.
+In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration.
 

### 2015-04-27 extension.Rmd
Extension rmd and html files

---
title: "Gozde and Liora extension"
author: "Liora Goldensher"
date: "April 27, 2015"
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---
# EXTENSION

Our extension was inspired by Andreas Wimmer and Yuval Feinstein's 2010 paper "The Rise of the Nation-State Across the World, 1816-2001."  This paper seperately tests the prevailing explanatory theories of the rise of the nation-state as the dominant form of governance. Our extension takes a similar approach, testing the major theories of support for extreme right parties in the Western European context in separate models. We operationalize the variables in these theories using the available measures from the original data set.

In order to obtain a compelling visual representation of the predictive power of different theories and models, we use the method suggested in Brian Greenhill, Michael D. Ward and Audrey Sacks (2011) "The Separation Plot: A New Visual Method for Evaluating the Fit of Models with Categorical Outcomes",  American Journal of Political Science 55 (3): 1-13. We use their R package "separationplot".

# Run necessary packages and load data (Source: Arzheimer dataverse)

```{r}

library(MASS)
library(nlme)
library(xtable)
library(foreign)
library(dplyr)
library(broom)
library(ggplot2)
library(xtable)
library(stargazer)
library(grid)
library(gridExtra)

data <- read.dta("nonimp.dta")

# Cleaning up data
data <- rename(data, ext_vote = rexvote)
data <- rename(data, age_1 = age1) # (18–29 years)
data <- rename(data, age_2 = age2) # (30–45 years)
data <- rename(data, age_4 = age4) # (>65 years)
data <- rename(data, edu_1 = mye1) # Education: middle/high
data <- rename(data, edu_2 = mye2) # Education: university
data <- rename(data, farmer_own = farmerown) 
data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
data <- rename(data, dispro_elect = disp) # Disproportionality
data <- rename(data, federalism = lfed1) # Decentralization
data <- rename(data, z_asylumseeker = zasylumseekers) 
data <- rename(data, z_unemp = zsur) # Unemployment rate
data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse

```

# Preparing data for analysis

```{r}
# Create centered variables for Saliance and Variance based on grand mean centering according to author

data <- data  %>% 
  mutate(salience_mean_c = (salienzmean - 3.84568)) %>% 
  mutate(var_c = rvar - 21.75423)

# Make male variable numeric
data <- data %>%
  mutate(male = as.numeric(male))

# Create a dummy variable for country (transform from character to factor variable)
data <- data %>%
  mutate(country = factor(sortcountry, labels = c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
```

# Model 1: Adorno Thesis (Personality Traits and Value Orientations)
The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.  We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale.

```{r}
library(separationplot)
library(Hmisc) 
library(zoom)

model_1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + country - 1, data = data)
summary(model_1)
actual <- model_1$y # Create vector with actual values for vote intention for extreme right parties

log.odds <- model_1$fitted.values # Create a vector with log-odd values
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
plot_model1
```

```

#Conclusion
There isn't a big range in the predicted probabilities of the model, therefore the predicted probabilities are not very helpful. Separation plot helps a lot to discern the predictive power of the model. As the events of extreme right vote intension increases as we move to the right (i.e. red lines cluster around the end of the graph), the model does a good job of estimating the likelihood of events. However, as the small arrow in the graph shows, the model predicts that half the number of observations will have the intention to vote for an extreme right party. The number of actual events (red lines) is much lower.

# Model 2: Parsons Thesis (Social Disintegration)
Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.  While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change that Parsons refers to: satisfaction with democracy and the negative evaluation of the European Union.

```{r}
model_2 <- glm(ext_vote ~ eu_neg + z_dem_satis + country - 1, data = data)
summary(model_2)

actual <- model_2$y # Create vector with actual values for vote intention for extreme right parties

log.odds <- model_2$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
plot_model2
```

#Conclusion:
Again, there is little variation in our predictive probabilities with this model. Similar to model 1, most events are aligned with higher predictive probabilities on the right hand of the graph. Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with event than non-events as in Model 2.

# Model 3: Group Conflict Model (Various theories)
Group conflict theories encompass a variety of theories.  Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits. Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.  In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration: unemployment rates, unemployment benefits, number of asylum seekers, saliance and variance of right-wing issues.

```{r}
model_3 <- glm(ext_vote ~ z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + country - 1, data = data)

summary(model_3)
actual <- model_3$y # Create vector with actual values for vote intention for extreme right parties

log.odds <- model_3$fitted.values # Create a function with log-odds
# Create link function to transform log-odds into predicted probabilities
link <- function(P) {
  1/(1+exp(-P))
} 
pred <- link(log.odds) # Transform log-odds into predicted probabilities
pred <- as.vector(pred) 
range(pred) # variation in the predicted probabilities: very little variation.
dev.off()
# Create separation plot to visualize the predictive power of the model
plot_model3 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
```

#Conclusion:
The majority of events (intention to vote for ER) are clustered at the end right end of the model - which is in line with a good predictive model. However, in this model the distribution of events is very dispersed compared to other two models.

Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.

### 2015-04-27 extension.Rmd
edited to remove long output

@@
 plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
-plot_model1
-```
-
 ```
@@
 The number of actual events (red lines) is much lower.
+
+```
 
@@
 plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
-plot_model2
 ```
@@
 Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with event than non-events as in Model 2.
+
+```
 

### 2015-04-27 replication project.Rmd

--- 2015-04-23 replication.Rmd
@@
----
 ---
@@
 Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood.
-Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables; we'll keep working on these.
+Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
 
@@
 library(msm)
-asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01)) # vector with possible values for asylumseekers
+asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers
 
@@
 ![Figure 2](figures/fig2.png)
+
 ```{r}
-# Graph 1
+
+# Figure 2, graph 1
 salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
@@
 
+# EXTENSION
+
+Our extension was inspired by Andreas Wimmer and Yuval Feinstein's 2010 paper "The Rise of the Nation-State Across the World, 1816-2001."  This paper seperately tests the prevailing explanatory theories of the rise of the nation-state as the dominant form of governance.
+Our extension takes a similar approach, testing the major theories of support for extreme right parties in the Western European context in separate models.
+We operationalize the variables in these theories using the available measures from the original data set.
+
+In order to obtain a compelling visual representation of the predictive power of different theories and models, we use the method suggested in Brian Greenhill, Michael D.
+Ward and Audrey Sacks (2011) "The Separation Plot: A New Visual Method for Evaluating the Fit of Models with Categorical Outcomes",  American Journal of Political Science 55 (3): 1-13.
+We use their R package "separationplot".
+
 # Model 1: Adorno Thesis (Personality Traits and Value Orientations)
+The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.
+We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale.
 
 ```{r}
-model1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+library(separationplot)
+library(Hmisc) 
+library(zoom)
+
+model_1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + country - 1, data = data)
+summary(model_1)
+actual <- model_1$y # Create vector with actual values for vote intention for extreme right parties
+
+log.odds <- model_1$fitted.values # Create a vector with log-odd values
+# Create link function to transform log-odds into predicted probabilities
+link <- function(P) {
+  1/(1+exp(-P))
+} 
+pred <- link(log.odds) # Transform log-odds into predicted probabilities
+pred <- as.vector(pred) 
+range(pred) # variation in the predicted probabilities: very little variation.
+dev.off()
+# Create separation plot to visualize the predictive power of the model
+plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+plot_model1
+```
 
@@
 
+#Conclusion
+There isn't a big range in the predicted probabilities of the model, therefore the predicted probabilities are not very helpful.
+Separation plot helps a lot to discern the predictive power of the model.
+As the events of extreme right vote intension increases as we move to the right (i.e.
+red lines cluster around the end of the graph), the model does a good job of estimating the likelihood of events.
+However, as the small arrow in the graph shows, the model predicts that half the number of observations will have the intention to vote for an extreme right party.
+The number of actual events (red lines) is much lower.
+
 # Model 2: Parsons Thesis (Social Disintegration)
+Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.
+While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change that Parsons refers to: satisfaction with democracy and the negative evaluation of the European Union.
+
 ```{r}
-model2 <- glm(ext_vote ~ eu_neg + z_dem_satis + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+model_2 <- glm(ext_vote ~ eu_neg + z_dem_satis + country - 1, data = data)
+summary(model_2)
+
+actual <- model_2$y # Create vector with actual values for vote intention for extreme right parties
+
+log.odds <- model_2$fitted.values # Create a function with log-odds
+# Create link function to transform log-odds into predicted probabilities
+link <- function(P) {
+  1/(1+exp(-P))
+} 
+pred <- link(log.odds) # Transform log-odds into predicted probabilities
+pred <- as.vector(pred) 
+range(pred) # variation in the predicted probabilities: very little variation.
+dev.off()
+# Create separation plot to visualize the predictive power of the model
+plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+plot_model2
 ```
 
+#Conclusion:
+Again, there is little variation in our predictive probabilities with this model.
+Similar to model 1, most events are aligned with higher predictive probabilities on the right hand of the graph.
+Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with event than non-events as in Model 2.
+
 # Model 3: Group Conflict Model (Various theories)
+Group conflict theories encompass a variety of theories.
+Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits.
+Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.
+In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration: unemployment rates, unemployment benefits, number of asylum seekers, saliance and variance of right-wing issues.
 
 ```{r}
-model3 <- glm(ext_vote ~ dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
+model_3 <- glm(ext_vote ~ z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + country - 1, data = data)
 
+summary(model_3)
+actual <- model_3$y # Create vector with actual values for vote intention for extreme right parties
+
+log.odds <- model_3$fitted.values # Create a function with log-odds
+# Create link function to transform log-odds into predicted probabilities
+link <- function(P) {
+  1/(1+exp(-P))
+} 
+pred <- link(log.odds) # Transform log-odds into predicted probabilities
+pred <- as.vector(pred) 
+range(pred) # variation in the predicted probabilities: very little variation.
+dev.off()
+# Create separation plot to visualize the predictive power of the model
+plot_model3 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
 ```
+
+#Conclusion:
+The majority of events (intention to vote for ER) are clustered at the end right end of the model - which is in line with a good predictive model.
+However, in this model the distribution of events is very dispersed compared to other two models.
+
+Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.

### 2015-04-27 extension.Rmd
Extension final version

@@
 title: "Gozde and Liora extension"
-author: "Liora Goldensher"
+author: "Liora and Gozde"
 date: "April 27, 2015"
@@
 library(Hmisc)
-library(zoom)
 
@@
 # Create separation plot to visualize the predictive power of the model
-plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
 ```
+
+![Model 1](figures/SP.Model1.png)
 
@@
 # Model 2: Parsons Thesis (Social Disintegration)
+
 Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.
@@
 # Create separation plot to visualize the predictive power of the model
-plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
 ```
+
+![Model 2](figures/SP.model2.png)
 
@@
 # Model 3: Group Conflict Model (Various theories)
+
 Group conflict theories encompass a variety of theories.
@@
 # Create separation plot to visualize the predictive power of the model
-plot_model3 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
 ```
+
+![Model 3](figures/SP.model3.png)
 
@@
 
+All Three Models
+
+![Model 1](figures/SP.Model1.png)
+
+![Model 2](figures/SP.model2.png)
+
+![Model 3](figures/SP.model3.png)
+
 Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.

### 2015-04-28 replication project.Rmd
Updated and combined replication code with extension

@@
 
-Note: Please refer to saved files in our repository for images from the article.
-Also please refer to the table and figures (Table 1, Figure 1, 2) in the repository.
-Image scales are rearranged in saved versions.
-Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood.
-Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
+Note: Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood.
+Finally, we were unfortunately not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
 
@@
 Kai Arzheimer, "Contextual Factors and the Extreme Right Vote in Western Europe, 1980-2002"25548117.pdf
-This article attempts to answer the “twin question of why the extreme right support is so unstable within many countries over time, and why these parties are so weak in many West European countries.” Authors conduct a multi-level analysis, combining data on macro-level contextual variables (unemployment, immigration, and welfare benefits) with individual-level variables (sociodemographic factors and attitudes).
+This article attempts to answer the “twin question of why the extreme right support is so unstable within many countries over time, and why these parties are so weak in many West European countries.” The author conduct a multi-level analysis, combining data on macro-level contextual variables (unemployment, immigration, and welfare benefits) with individual-level variables (sociodemographic factors and attitudes).
+It concludes that although the contextual factors are positively correlated with the intention to vote for an extreme-right party, they don't seem to reinforce each other (i.e.
+as unemployment levels rise, the effect of immigration does not increase but rather declines).
 
@@
 #The model 
-The article uses a logistic multi-level model via Penalized Quasi-Likelihood. The dependent variable is vote intention for an extreme right party, which is assumed to be binomially distributed.
+The article uses a multi-level logistic model via Penalized Quasi-Likelihood. The dependent variable is vote intention for an extreme right party, which is assumed to be binomially distributed.
 
@@
 ```{r}
-
 # Figure 2, graph 1
-salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
+# Create vector with possible values for salience
+salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by = .1) 
 variable <- salience
@@
 graph_4
-`
 ```
@@
 
+Run necessary packages and load data (Source: Arzheimer dataverse)
+
+```{r}
+
+library(MASS)
+library(nlme)
+library(xtable)
+library(foreign)
+library(dplyr)
+library(broom)
+library(ggplot2)
+library(xtable)
+library(stargazer)
+library(grid)
+library(gridExtra)
+
+data <- read.dta("nonimp.dta")
+
+# Cleaning up data
+data <- rename(data, ext_vote = rexvote)
+data <- rename(data, age_1 = age1) # (18–29 years)
+data <- rename(data, age_2 = age2) # (30–45 years)
+data <- rename(data, age_4 = age4) # (>65 years)
+data <- rename(data, edu_1 = mye1) # Education: middle/high
+data <- rename(data, edu_2 = mye2) # Education: university
+data <- rename(data, farmer_own = farmerown) 
+data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
+data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
+data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
+data <- rename(data, dispro_elect = disp) # Disproportionality
+data <- rename(data, federalism = lfed1) # Decentralization
+data <- rename(data, z_asylumseeker = zasylumseekers) 
+data <- rename(data, z_unemp = zsur) # Unemployment rate
+data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
+data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse
+
+```
+
+# Preparing data for analysis
+
+```{r}
+# Create centered variables for Saliance and Variance based on grand mean centering according to author
+
+data <- data  %>% 
+  mutate(salience_mean_c = (salienzmean - 3.84568)) %>% 
+  mutate(var_c = rvar - 21.75423)
+
+# Make male variable numeric
+data <- data %>%
+  mutate(male = as.numeric(male))
+
+# Create a dummy variable for country (transform from character to factor variable)
+data <- data %>%
+  mutate(country = factor(sortcountry, labels = c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
+```
+
 # Model 1: Adorno Thesis (Personality Traits and Value Orientations)
@@
 # Create separation plot to visualize the predictive power of the model
-plot_model1 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
-plot_model1
+separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
 ```
 
-```
+![Model 1](figures/SP.Model1.png)
 
@@
 
+```
+
 # Model 2: Parsons Thesis (Social Disintegration)
+
 Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.
@@
 # Create separation plot to visualize the predictive power of the model
-plot_model2 <- separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
-plot_model2
+separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
 ```
+
+![Model 2](figures/SP.model2.png)
 
@@
 
+```
+
 # Model 3: Group Conflict Model (Various theories)
+
 Group conflict theories encompass a variety of theories.

### 2015-04-30 replication project.Rmd
FINAL VERSIONS - Separated replication and extension files

@@
 ```
-
-# EXTENSION
-
-Our extension was inspired by Andreas Wimmer and Yuval Feinstein's 2010 paper "The Rise of the Nation-State Across the World, 1816-2001."  This paper seperately tests the prevailing explanatory theories of the rise of the nation-state as the dominant form of governance.
-Our extension takes a similar approach, testing the major theories of support for extreme right parties in the Western European context in separate models.
-We operationalize the variables in these theories using the available measures from the original data set.
-
-In order to obtain a compelling visual representation of the predictive power of different theories and models, we use the method suggested in Brian Greenhill, Michael D.
-Ward and Audrey Sacks (2011) "The Separation Plot: A New Visual Method for Evaluating the Fit of Models with Categorical Outcomes",  American Journal of Political Science 55 (3): 1-13.
-We use their R package "separationplot".
-
-Run necessary packages and load data (Source: Arzheimer dataverse)
-
-```{r}
-
-library(MASS)
-library(nlme)
-library(xtable)
-library(foreign)
-library(dplyr)
-library(broom)
-library(ggplot2)
-library(xtable)
-library(stargazer)
-library(grid)
-library(gridExtra)
-
-data <- read.dta("nonimp.dta")
-
-# Cleaning up data
-data <- rename(data, ext_vote = rexvote)
-data <- rename(data, age_1 = age1) # (18–29 years)
-data <- rename(data, age_2 = age2) # (30–45 years)
-data <- rename(data, age_4 = age4) # (>65 years)
-data <- rename(data, edu_1 = mye1) # Education: middle/high
-data <- rename(data, edu_2 = mye2) # Education: university
-data <- rename(data, farmer_own = farmerown) 
-data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
-data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
-data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
-data <- rename(data, dispro_elect = disp) # Disproportionality
-data <- rename(data, federalism = lfed1) # Decentralization
-data <- rename(data, z_asylumseeker = zasylumseekers) 
-data <- rename(data, z_unemp = zsur) # Unemployment rate
-data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
-data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse
-
-```
-
-# Preparing data for analysis
-
-```{r}
-# Create centered variables for Saliance and Variance based on grand mean centering according to author
-
-data <- data  %>% 
-  mutate(salience_mean_c = (salienzmean - 3.84568)) %>% 
-  mutate(var_c = rvar - 21.75423)
-
-# Make male variable numeric
-data <- data %>%
-  mutate(male = as.numeric(male))
-
-# Create a dummy variable for country (transform from character to factor variable)
-data <- data %>%
-  mutate(country = factor(sortcountry, labels = c("AT", "BE","DE-E","DE-W","DK","ES","FI","FR","GR","IT","LU","NL","NO","PT","SE")))
-```
-
-# Model 1: Adorno Thesis (Personality Traits and Value Orientations)
-The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.
-We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale.
-
-```{r}
-library(separationplot)
-library(Hmisc)
-
-model_1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + country - 1, data = data)
-summary(model_1)
-actual <- model_1$y # Create vector with actual values for vote intention for extreme right parties
-
-log.odds <- model_1$fitted.values # Create a vector with log-odd values
-# Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
-} 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
-# Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
-```
-
-![Model 1](figures/SP.Model1.png)
-
-#Conclusion
-There isn't a big range in the predicted probabilities of the model, therefore the predicted probabilities are not very helpful.
-Separation plot helps a lot to discern the predictive power of the model.
-As the events of extreme right vote intension increases as we move to the right (i.e.
-red lines cluster around the end of the graph), the model does a good job of estimating the likelihood of events.
-However, as the small arrow in the graph shows, the model predicts that half the number of observations will have the intention to vote for an extreme right party.
-The number of actual events (red lines) is much lower.
-
-```
-
-# Model 2: Parsons Thesis (Social Disintegration)
-
-Parsons' 1942 theory of social disintegration posits that anomia, a breakdown of social norms, and attendant feelings of anxiety, anger and isolation brings about a longing for strong leadership and rigid ideologies that extreme right parties can provide.
-While we do not have measures for the emotions of participants in the studies whose data we use, in our second model we examine the relationship between extreme right voting and the kinds of sentiments about social change that Parsons refers to: satisfaction with democracy and the negative evaluation of the European Union.
-
-```{r}
-model_2 <- glm(ext_vote ~ eu_neg + z_dem_satis + country - 1, data = data)
-summary(model_2)
-
-actual <- model_2$y # Create vector with actual values for vote intention for extreme right parties
-
-log.odds <- model_2$fitted.values # Create a function with log-odds
-# Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
-} 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
-# Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
-```
-
-![Model 2](figures/SP.model2.png)
-
-#Conclusion:
-Again, there is little variation in our predictive probabilities with this model.
-Similar to model 1, most events are aligned with higher predictive probabilities on the right hand of the graph.
-Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with event than non-events as in Model 2.
-
-```
-
-# Model 3: Group Conflict Model (Various theories)
-
-Group conflict theories encompass a variety of theories.
-Some emphasize the role of instrumental rationality, arguing that xenophobia results from a contest between immigrants and residents over scarce resources like jobs and welfare benefits.
-Others emphasize the scapegoating of immigrants as perceived threats to residents' status, power or resources.
-In this last model, we use relevant variables representing both the availability of resources like jobs and welfare benefits and the prevalence of immigration: unemployment rates, unemployment benefits, number of asylum seekers, saliance and variance of right-wing issues.
-
-```{r}
-model_3 <- glm(ext_vote ~ z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + country - 1, data = data)
-
-summary(model_3)
-actual <- model_3$y # Create vector with actual values for vote intention for extreme right parties
-
-log.odds <- model_3$fitted.values # Create a function with log-odds
-# Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
-} 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
-# Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
-```
-
-![Model 3](figures/SP.model3.png)
-
-#Conclusion:
-The majority of events (intention to vote for ER) are clustered at the end right end of the model - which is in line with a good predictive model.
-However, in this model the distribution of events is very dispersed compared to other two models.
-
-All Three Models
-
-![Model 1](figures/SP.Model1.png)
-
-![Model 2](figures/SP.model2.png)
-
-![Model 3](figures/SP.model3.png)
-
-Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.

### 2015-04-30 extension.Rmd

@@
 
-# Run necessary packages and load data (Source: Arzheimer dataverse)
+Run necessary packages and load data (Source: Arzheimer dataverse)
 
@@
 
-Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power.
+Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power given the level of concentration of events in the upper probabilities area in the plot.

### 2015-05-11 replication only.Rmd
Added citation for Harvard students' code, removed duplicate packages and added notation about purposes of various packages

--- 2015-04-23 replication.Rmd
@@
 
-library(MASS)
-library(nlme)
-library(xtable)
-library(foreign)
-library(dplyr)
-library(broom)
-library(ggplot2)
-library(xtable)
-library(stargazer)
-library(grid)
-library(gridExtra)
+library(MASS) #includes the glmmPQL function
+library(nlme) #for non-linear mixed effects models
+library(foreign) #allows us to read in data from another format
+library(dplyr) #allows us to manipulate our dataset
+library(broom) #helps tidy data and present in a more usable form
+library(ggplot2) #for graphing
+library(xtable) #???
+library(stargazer) #used to create Table 1
+library(grid) #used to combine ggplot graphs
+library(gridExtra) #used to combine ggplot graphs
 
@@
 # Preparing data for analysis
+#lines 62-83 of this code are based on (though not identical to) the code written by Harvardstudents in their previous replication of this paper.
+Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1 [Version]
 
@@
 ```
-
-# Model 1: Adorno Thesis (Personality Traits and Value Orientations)
-
-```{r}
-model1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
-
-```
-
-# Model 2: Parsons Thesis (Social Disintegration)
-```{r}
-model2 <- glm(ext_vote ~ eu_neg + z_dem_satis + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
-```
-
-# Model 3: Group Conflict Model (Various theories)
-
-```{r}
-model3 <- glm(ext_vote ~ dispro_elect + federalism + z_asylumseeker + z_unemp + z_asylumseeker:z_unemp + z_replacement + z_replacement:z_unemp + z_replacement:z_asylumseeker + max_er + salience_mean_c + var_c + var_c:salience_mean_c + country - 1)
-
-```

### 2015-05-11 replication only.Rmd
Wrote function for graphs

@@
 # Preparing data for analysis
-#lines 62-83 of this code are based on (though not identical to) the code written by Harvardstudents in their previous replication of this paper.
+#lines 64-83 of this code are based on (though not identical to) the code written by Harvard students in their previous replication of this paper.
 Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1 [Version]
@@
 ```{r}
-library(msm)
+library(msm) #includes deltamethod function, which allows us to obtain standard errors of transformed parameters
+#Function with which we will create each graph
+graph <- function(data, ratio, ymin, ymax) {
+  ggplot(data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + #color will always be blue
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") + #fixed y intercept and color
+  labs(x = xtitle, y = ytitle, title = main) + #titles will call from prepared data
+  coord_fixed(ratio)
+}
+#Preparing the data for the first graph
 asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers
@@
 variable.data <- cbind(variable, slopes, upper, lower)
-
-# Creating the first graph with ggplot
-
 variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
@@
 main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
-graph_1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main) +
-  coord_fixed(ratio = 8)
+
+#creating the first graph using our ggplot function
+graph_1 <- graph(data = variable.data, ratio = 8)
+graph_1
 
@@
 
+#Preparing the data for the second graph
 unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
@@
 variable.data <- cbind(variable, slopes, upper, lower)
-
-# Creating the second graph with ggplot:
-
 variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
@@
 main <- "The Conditional Effects of Unemployment and Immigration"
-graph_2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle) +
-  coord_fixed(ratio = 12)
+#Creating the second graph with our function
+graph_2 <- graph(data = variable.data, ratio = 12)
+graph_2
 
@@
 # Figure 2, graph 1
+#Preparning the data to graph
 salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
@@
 variable.data <- cbind(variable, slopes, upper, lower)
-
-# Creating the first graph with ggplot:
-
 variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
@@
 main <- "The Conditional Effects of Salience and Variance"
-graph_3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main) +
-  coord_fixed(ratio = 400)
+
+#Creating the first graph with our function
+graph_3 <- graph(data = variable.data, ratio = 400)
+graph_3
 
 # Second part of Figure 2:
-
+#Preparing the data to graph
 variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
@@
 main <- "The Conditional Effects of Salience and Variance"
-graph_4 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main) +
-  coord_fixed(ratio = 500)
+
+#Creating the second graph with our function
+graph_4 <- graph(data = variable.data, ratio = 500)
+graph_4
 

### 2015-05-11 replication project.Rmd
edits and improvements

@@
 ---
-title: "Gozde and Liora Replication Code"
+title: "Gozde and Liora's Replication Code"
 author: "Gozde Guran and Liora Goldensher"
@@
 
-library(MASS)
-library(nlme)
-library(xtable)
-library(foreign)
-library(dplyr)
-library(broom)
-library(ggplot2)
-library(xtable)
-library(stargazer)
-library(grid)
-library(gridExtra)
+library(MASS) # includes the glmmPQL function to run model
+library(nlme) # for non-linear mixed effects models
+library(foreign) # allows us to read in data from another format
+library(dplyr) # allows us to manipulate our dataset
+library(broom) # helps tidy data and present in a more usable form
+library(ggplot2) # for graphing
+library(stargazer) # used to create regression tables
+library(grid) # used to combine ggplot graphs
+library(gridExtra) # used to combine ggplot graphs
+library(msm) #includes deltamethod function, which allows us to obtain standard errors of transformed parameters
 
@@
 # Cleaning up data
-data <- rename(data, ext_vote = rexvote)
-data <- rename(data, age_1 = age1) # (18–29 years)
-data <- rename(data, age_2 = age2) # (30–45 years)
-data <- rename(data, age_4 = age4) # (>65 years)
-data <- rename(data, edu_1 = mye1) # Education: middle/high
-data <- rename(data, edu_2 = mye2) # Education: university
-data <- rename(data, farmer_own = farmerown) 
-data <- rename(data, left_right_scale = zlrs) # Left-Right Scale
-data <- rename(data, eu_neg = euschlecht) # Negative evaluation of EU membership of one's own country
-data <- rename(data, z_dem_satis = zsatisdmo) # Dissatisfied: Democracy
-data <- rename(data, dispro_elect = disp) # Disproportionality
-data <- rename(data, federalism = lfed1) # Decentralization
-data <- rename(data, z_asylumseeker = zasylumseekers) 
-data <- rename(data, z_unemp = zsur) # Unemployment rate
-data <- rename(data, z_replacement = zreplacementrate) # Unemp benefits
-data <- rename(data, max_er = rmax) # Maximum toughness in extreme right discourse
-
+data <- data %>%
+  rename(ext_vote = rexvote,
+         age_1 = age1, # (18–29 years)
+         age_2 = age2, # (30–45 years)
+         age_4 = age4, # (>65 years)
+         edu_1 = mye1, # Education: middle/high
+         edu_2 = mye2, # Education: university
+         farmer_own = farmerown,
+         left_right_scale = zlrs, # Left-Right Scale
+         eu_neg = euschlecht, # Negative evaluation of EU membership of one's own country
+         z_dem_satis = zsatisdmo, # Dissatisfied: Democracy
+         dispro_elect = disp, # Disproportionality
+         federalism = lfed1, # Decentralization
+         z_asylumseeker = zasylumseekers,
+         z_unemp = zsur, # Unemployment rate
+         z_replacement = zreplacementrate, # Unemp benefits
+         max_er = rmax) # Maximum toughness in extreme right discourse
 ```
@@
 # Preparing data for analysis
+Lines 64-83 of this code are based on (though not identical to) the code written by Harvard students in their previous replication of this paper.
+Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1
 
@@
 ```{r}
-# Create vectors of coefficients, standard deviations, and variable names
+# Create vectors of coefficients, standard errors, and variable names
 
 coefficient <- as.vector(model$coef$fixed) 
-n <- c(174452, 267)
-stand_dev <- as.vector(sqrt(diag(model$varFix)))
+standard_error <- as.vector(sqrt(diag(model$varFix)))
 
 # Create matrix of coefficients and standard deviations.
-
-table_matrix <- cbind(coefficient, stand_dev)
+table_matrix <- cbind(coefficient, standard_error)
 
@@
 
-table_1 <- stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model.
+stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", type = "text", notes = "Logistic multilevel model.
 PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
-
 ```
@@
 ```{r}
-library(msm)
+#Function with which we will create each graph
+graph <- function(data, ratio, ymin, ymax) {
+  ggplot(data, aes(x = variable, y = slopes)) + 
+  geom_line(aes(y = slopes), color = "blue") + #color will always be blue
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
+  geom_hline(yintercept = 0, size = 0.4, color = "black") + #fixed y intercept and color
+  labs(x = xtitle, y = ytitle, title = main) + #titles will call from prepared data
+  coord_fixed(ratio)
+}
+#Preparing the data for the first graph
 asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers
-
 variable <- asy # identifying "asy" as the variable of interest so that the remaining code can be reused in the next graph with a different variable of interest specified
-slopes <- model$coef$fixed["z_unemp"] + model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
+slopes <- model$coef$fixed["z_unemp"] + 
+  model$coef$fixed["z_asylumseeker:z_unemp"] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
 estmean <- model$coef$fixed # Estimated means for each variable 
@@
 main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
-graph_1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle, title = main) +
-  coord_fixed(ratio = 8)
 
-#Figure 1, graph 2
+#creating the first graph using our ggplot function
+graph_1 <- graph(data = variable.data, ratio = 8)
+graph_1
 
+#Preparing the data for the second graph
 unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
@@
 main <- "The Conditional Effects of Unemployment and Immigration"
-graph_2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
-  geom_line(aes(y = slopes), color = "blue") + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
-  geom_hline(yintercept = 0, size = 0.4, color = "black") +
-  labs(x = xtitle, y = ytitle) +
-  coord_fixed(ratio = 12)
+#Creating the second graph with our function
+graph_2 <- graph(data = variable.data, ratio = 12)
+graph_2
 
 # Figure 1 with ggplot
-
 grid.arrange(graph_1, graph_2, ncol = 1)
@@
 graph_2
-
 ```
@@
 # Figure 2, graph 1
-# Create vector with possible values for salience
-salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by = .1) 
+#Preparning the data to graph
+salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
 variable <- salience

### 2015-05-11 extension.Rmd

@@
 ---
-title: "Gozde and Liora extension"
+title: "Gozde and Liora Extension Project"
 author: "Liora and Gozde"
@@
 ---
-# EXTENSION
 
@@
 library(nlme)
-library(xtable)
 library(foreign)
@@
 library(ggplot2)
-library(xtable)
 library(stargazer)
@@
 library(gridExtra)
+library(separationplot)
+library(Hmisc)
 
@@
 
-# Model 1: Adorno Thesis (Personality Traits and Value Orientations)
+# Model 1: Adorno Thesis (Individual Characteristics and Value Orientations)
 The first model is based on Theodor Adorno's 1950 theory that support for extreme right parties (in his case, fascist parties) originates from supporters' personality traits and value orientations, which make individuals more receptive to the appeals of extreme right parties.
@@
 ```{r}
-library(separationplot)
-library(Hmisc)
-
 model_1 <- glm(ext_vote ~ male + age_1 + age_2 + age_4 + edu_1 + edu_2 + farmer_own + worker + retired + unemployed + partner + left_right_scale + country - 1, data = data)
@@
 # Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
+link <- function(log.odd) {
+  pred.prob <- 1/(1+exp(-log.odd))
+  pred.prob # returns a numeric vector of predicted probabilities
 } 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
+pred_prob <- link(log.odds) # Transform log-odds into predicted probabilities
+pred_prob <- as.vector(pred_prob) 
+range(pred_prob) # variation in the predicted probabilities: very little variation.
+# Graph variation in Predicted probabilities
+pred_df <- data.frame(pred_prob)
+ggplot(pred_df, aes(x = 1:length(pred_prob), y = pred_prob)) + 
+  geom_line() +
+  xlab("Prediction Number") +
+  ylab("Predicted Probability") +
+  ggtitle("Model 1: Variation in Predicted Probabilities")
 # Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
+separationplot(pred = pred_prob, actual = actual, type = "rect", heading = "Model1: The Adorno Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
 ```
@@
 actual <- model_2$y # Create vector with actual values for vote intention for extreme right parties
-
 log.odds <- model_2$fitted.values # Create a function with log-odds
-# Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
-} 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
+pred_prob <- link(log.odds) # Transform log-odds into predicted probabilities
+pred_prob <- as.vector(pred_prob) 
+range(pred_prob) # variation in the predicted probabilities: very little variation.
+# Visualize variation in predicted probabilities
+pred_df <- data.frame(pred_prob)
+ggplot(pred_df, aes(x = 1:length(pred_prob), y = pred_prob)) + 
+  geom_line() +
+  xlab("Prediction Number") +
+  ylab("Predicted Probability") +
+  ggtitle("Model 2: Variation in Predicted Probabilities")
 # Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T) 
+separationplot(pred = pred_prob, actual = actual, type = "rect", heading = "Model2: The Parsons Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
 ```
@@
 Similar to model 1, most events are aligned with higher predictive probabilities on the right hand of the graph.
-Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with event than non-events as in Model 2.
+Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with events rather than non-events as in Model 2.
 
@@
 
+We used interactions between contextual variables in this model in line with the author's original model.
+
 ```{r}
@@
 log.odds <- model_3$fitted.values # Create a function with log-odds
-# Create link function to transform log-odds into predicted probabilities
-link <- function(P) {
-  1/(1+exp(-P))
-} 
-pred <- link(log.odds) # Transform log-odds into predicted probabilities
-pred <- as.vector(pred) 
-range(pred) # variation in the predicted probabilities: very little variation.
-dev.off()
+pred_prob <- link(log.odds) # Transform log-odds into predicted probabilities
+pred_prob <- as.vector(pred_prob) 
+range(pred_prob) # variation in the predicted probabilities: very little variation.
+# Visualize variation in predicted probabilities
+pred_df <- data.frame(pred_prob)
+ggplot(pred_df, aes(x = 1:length(pred_prob), y = pred_prob)) + 
+  geom_line() +
+  xlab("Prediction No") +
+  ylab("Predicted Probability") +
+  ggtitle("Model 3: Variation in Predicted Probabilities")
 # Create separation plot to visualize the predictive power of the model
-separationplot(pred = pred, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
+separationplot(pred = pred_prob, actual = actual, type = "rect", heading = "Model3: The Group Conflict Thesis", xlab = "ER Vote Intention", newplot = F, line = T, lwd2 = 0.8, height = 0.5, show.expected = T)
 ```
@@
 #Conclusion:
-The majority of events (intention to vote for ER) are clustered at the end right end of the model - which is in line with a good predictive model.
-However, in this model the distribution of events is very dispersed compared to other two models.
+The majority of events (the intention to vote for an extreme right party) is clustered at the right end of the model - which is in line with a good predictive model.
+However, in this model the distribution of events is very dispersed compared to the other two models.
 

### 2015-05-12 response_to_reviewers.Rmd

---
title: "response_to_reviewers"
author: "Gozde and Liora"
date: "5/12/2015"
output: html_document
---

We thank all four reviewers for providing excellent feedback on our replication and extension code. Most of their suggestions were related to improving our code, which we adopted whenever possible. Our reviewers also commented on the theoretical and modelling decisions in our code, and we tried to address these points below.

Replication Edits:

1) Following Aaron and Andres's recommendation, we used pipes in our data cleaning code, specifically in the code to rename a number of variables in the data frame (lines 41-58). Since we didn't change all 83 variable names, the "rename" function rather than dplyr's "select" command  was more practical. This change made our code much more simple to edit and easier to follow through. 
2) As per Aaron and Andres's suggestion, we added documentation on the packages we are using in our replication. 
3) We agree with Angela and Matt's comments on the hard-coded numbers for centered variables (lines 67-69): We acknowledge that this is not good coding practice; however, due to our difficulty in reading the author's original code in Stata, we were unable to reproduce these numbers via our own code in R. Our efforts to find how the author calculated grand-mean centering for these two variables could not yield these results so we used the hard-coded numbers.
4) Per Matt and Angela's suggestions, we have created a function to plot all four of the graphs.  In addition to making the code somewhat more concise, this makes our code more self-documenting in that it highlights the similar structures of these graphs.

Extension Edits:

1) We improved our logit link function in line with Matt's comment (line 93): we gave better names for arguments and outputs; we removed redundant code which created the link function for each model. 
2) Following Matt's suggestion (line 95), we graphed the range in predicted probabilities to better present the very little variation in predictions for all three models. The differences between the graphs for each model also made us realize the connection between plotted probabilities and the separation plots. 
3) Per Andres's comment (line 144) about the use of interactions in model 3, we added furher documentation. Here we decided to use interactions between contextual variables following the author's original model. 
4) Following Matt's question about the multi-level model, we added a note on this point. While we were interested in visualizing the predictive power of all three theories in our extension, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze extreme-right vote intention for each individual.

### 2015-05-12 extension.Rmd
updated with more edits

@@
 The number of actual events (red lines) is much lower.
-
 ```
@@
 Yet Model 1 has slightly better predictive power as the very end of the graph is likely to be clustered with events rather than non-events as in Model 2.
-
-```
 
@@
 Although there is very little difference in the separation plots for all three models, our conclusion is that model 1 (the Adorno thesis which emphasizes individual-level characteristics and personal attitudes) has the most predictive power given the level of concentration of events in the upper probabilities area in the plot.
+
+This extension breaks Arzheimer's multi-level model into three different models that correspond to the three theoretical explanations for political orientation towards extreme right parties and movements.
+While we were interested in visualizing the predictive power of each theory, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze ER vote intension.
+That said, we think treating each country as another level that the election contexts are nested in (rather than taking countries as dummy variables) would have provided an even more compelling multi-level model.

### 2015-05-12 replication project.Rmd
Added note line 11

@@
 Finally, we were unfortunately not able to reproduce the last two figures that showed the joint impact of more than 2 variables.
+These graphs are dependant on a concept called "covariate contributions" developed by Mitchell and Chen (2005), that represents the aggregation into a single quantity of individual effects of all independant variables that are not varied in a graph.
+Graphs based on this concept were beyond the scope of our understanding or ability for this project.
 

### 2015-05-12 extension.Rmd
Added interpretation sentence, residuals plots

@@
          federalism = lfed1, # Decentralization
-         z_asylumseeker = zasylumseekers,
+         z_asylumseeker = zasylumseekers ,
          z_unemp = zsur, # Unemployment rate
@@
 We operationalize "personality traits and value orientations" using the individual level characteristics from our data set: gender, age, occupation, marital status, and self-placement on a left-right scale.
+These variables are rather poor proxies for "personality traits and value orientations", but provide the closest approximation from our dataset.
 
@@
 
-All Three Models
+# Diagnostics on our three models #
+The unit of analysis in each model is the individual. We wanted to apply a number of diagnostics to further test the predictive power of each model.
+
+For model 1, we first plot fitted values vs.
+residuals.
+Since we have a categorical outcome, binned residual plots are more informative than regular plots for fitted values vs.
+residuals.
+Here we benefited greatly from this Stackexchange post: http://stats.stackexchange.com/questions/63566/unexpected-residuals-plot-of-mixed-linear-model-using-lmer-lme4-package-in-r.
+Then, we extract the predicted probability for an example case: a young unemployed single male who self-identifies as right-wing in Austria.
+
+```{r}
+plot(fitted(model_1), residuals(model_1),
+  xlab = "Fitted Values", ylab = "Residuals")
+  abline(h=0, lty=2) # Not very useful since the outcome is a catogorical variable and is not distributed normally.
+
+library(arm) # To create binned plots for logistic models
+binnedplot(predict(model_1), resid(model_1), cex.pts=1, col.int="black")
+
+data_model1 <- data.frame(male = 1, age_1 = 1, age_2 = 0, age_4 = 0, edu_1 = 1, edu_2 = 0, farmer_own = 0, worker = 0, retired = 0, unemployed = 1, partner = 0, left_right_scale = max(data$left_right_scale, na.rm = T), country = "AT")
+
+predict(model_1, data_model1, type = "response")
+```
+
+For model 2, we again plot residuals vs.
+fitted values.
+This time the predictions are clustered on the left side.
+We then extract the predicted probability for an individual who disapproves of EU and is not satisfied with democracy.
+
+```{r}
+
+plot(fitted(model_2), residuals(model_2),
+  xlab = "Fitted Values", ylab = "Residuals")
+  abline(h=0, lty=2)
+
+binnedplot(predict(model_2), resid(model_2), cex.pts=1, col.int="black")
+
+data_model2 <- data.frame(eu_neg = max(data$eu_neg, na.rm = T), z_dem_satis = max(data$z_dem_satis, na.rm = T), country = "AT")
+
+predict(model_2, data_model2, type = "response")
+```
+
+For model 3, after plotting fitted values vs.
+residuals, we look for predicted probability for an individual whose context of unemployment rates, unemployment benefits, number of asylum seekers, and salience and variance of right-wing issues is Austria's most extreme--most likely to vote for an extreme right party, according to the theory.
+
+```{r}
+plot(fitted(model_3), residuals(model_3),
+  xlab = "Fitted Values", ylab = "Residuals")
+  abline(h=0, lty=2)
+
+binnedplot(predict(model_3), resid(model_3), cex.pts=1, col.int="black")
+
+#max_z_asylumseekers <- max(data$z_asylumseeker, na.rm = T) #4.45935
+#max_z_unemp <- max(data$z_unemp, na.rm = T) #12.2919
+#max_z_asylumseeker_z_unemp <- max(data$z_asylumseeker:data$z_unemp, na.rm = T) #-0.2445196
+#max_z_replacement <- max(data$z_replacement, na.rm = T) #32.96374
+#max_z_replacement_z_unemp <- max(data$z_replacement:data$z_unemp, na.rm = T) #0.5738534
+#max_z_replacement_z_asylumseeker <- max(data$z_replacement:data$z_asylumseeker, na.rm = T) #0.5738534
+
+#data_model3 <- data.frame(max_z_asylumseekers, max_z_unemp, max_z_asylumseeker_z_unemp, max_z_replacement, max_z_replacement_z_unemp, max_z_replacement_z_asylumseeker, country = "AT")
+#predict(model_3, data_model3, type = "response")
+#We have thus far been unable to debug the above code such that we could generate a prediction.  However, we do have a binned residual plot for this model
+```
+
+The binned residual plots show the highest level of randomness for the second and third models, Parsons' and the group conflict theories.
+This method would indicate that, contrary to our conclusions from the separation plots (see below), these models have the closest fit to the observed data.
+However, all of these conclusions must be qualified:  the proxy variables available to us in this data set do not perfectly operationalize the theoretical models in question.
+
+Conclusion: All Three Models
 

### 2015-05-13 response_to_reviewers.Rmd

@@
 While we were interested in visualizing the predictive power of all three theories in our extension, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze extreme-right vote intention for each individual.
+
+5) In response to Matt's suggestion, we attempted (with varying levels of success) other diagnostics on our three models.
+We created binned residuals plots and also attempted to compare predicted probabilities for extreme cases.
+
+Attempting these edits has improved both our code and our thinking about the theoretical and empirical puzzles in this paper.
+Again, many thanks to all the reviewers for their comments and suggestions.
